MP MetaAnalysis

### 2018-01-30 Analyses.Rmd
CogSci final prep; publication bias markdown file

sum_dat <- dat[!duplicated(dat[c("short_cite", "same_infant")]),]
time_wind_dat <- dat[!duplicated(dat[c("short_cite", "offset", "post_nam_dur")]),]

@@

@@

```{r DistractorType}

>>>>

sum_dat <- dat[!duplicated(dat[c("short_cite", "same_infant")]),]
time_wind_dat <- dat[!duplicated(dat[c("short_cite", "offset", "post_nam_dur")]),]
distract_dat <- dat[!duplicated(dat[c("short_cite", "object_pair")]),]

@@

This is a summary of the type of distractor used in an experiment

```{r DescriptivesDISTRACT, echo = FALSE}
#What kind of distractor was used?

distr_info <- distract_dat %>%
  group_by(object_pair) %>%
  summarize(count = n())

kable(distr_info)

@@

rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~condition*as.factor(object_pair), data = dat, random = ~ collapse | short_cite)

summary(rma_Distractor)

## Type of Distractor with age
```{r DistractorTypeAge}
